Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
starting to edit quiescent example

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow} 
We consider the suspension of two identical two-dimensional vesicles
suspended in a quiescent flow.  Without any external forcing such as an imposed
electric field or a fluid flow in the far-field, the long-range
attraction pulls two vesicles together until their separation distance
is close to $\delta$ and large deformation occurs in the ``contact region". The L.-J. type potential prohibits
physical contact between two membranes and instead keep them close to the separation distance $\delta$.
In Section~\ref{subsec:qflow_draining_times}, we
compute the expected time for the vesicles to reach an equilibrium
configuration and compare the analysis with numerical simulations.  In
Section~\ref{subsec:qflow_adhesion_parameters}, we characterize the
effects of the adhesion parameters and the vesicles' reduced area on the
bending and adhesive energies.

@@

\subsection{Effects of the adhesion parameters on equilibrium
configuration of a vesicle pair}
\label{subsec:qflow_adhesion_parameters} 
We next simulate a pair of identical two-dimensional vesicles
interacting with each other via the adhesion force in
equation~\eqref{eq:Fh}.  The initial vesicle placement is smaller than
in the previous simulations so that the equilibrium configuration is
achieved with a shorter timer horizon.  Once a vesicle doublet is
formed, the membrane shape in the contact region depends on the adhesion
strength relative to the membrane bending rigidity.  For weak to
moderate adhesion strength, vesicle membranes are flattened in the
contact region while the rest of vesicle maintains a nearly spherical
shape~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
Book_IntermolecularSurfaceForces,
RamachandranAndersonLealIsraelachvili2010_Langmuir}.  Under a strong
adhesion, however, the vesicle membranes in the contact region buckle
and form a sigmoidal shape  that has been observed in RBC doublet as
well~\cite{Ziherl2007_PRL, ZiherlSvetina2007_PNAS,
FlormannAouane2017_SciReports}.  An external electric field is also able
to buckle a vesicle membrane that is adhered to a solid
substrate~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow} 
We consider the suspension of two identical two-dimensional vesicles
suspended in a quiescent flow.  Without any external forcing such as an
imposed electric field or a fluid flow in the far-field, the long-range
attraction pulls two vesicles together until their separation distance
is close to $\delta$. The L.-J.~type potential prohibits physical
contact between two membranes and instead keep them close to the
separation distance $\delta$.  In
Section~\ref{subsec:qflow_draining_times}, we compute the expected time
for the vesicles to reach an equilibrium configuration and compare the
analysis with numerical simulations.  In
Section~\ref{subsec:qflow_adhesion_parameters}, we characterize the
effects of the adhesion parameters and the vesicles' reduced area on the
bending and adhesive energies.

@@

\subsection{Effects of the adhesion parameters on equilibrium
configuration of a vesicle pair}
\label{subsec:qflow_adhesion_parameters} 
We next simulate a pair of identical two-dimensional vesicles
interacting with each other via the adhesion force in
equation~\eqref{eq:Fh}.  The initial vesicle placement is smaller than
in the previous simulations so that the equilibrium configuration is
achieved with a shorter time horizon.  Once a vesicle doublet is
formed, the membrane shape in the contact region depends on the adhesion
strength relative to the membrane bending rigidity.  For weak to
moderate adhesion strength, vesicle membranes are flattened in the
contact region while the rest of vesicle maintains a nearly spherical
shape~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
Book_IntermolecularSurfaceForces,
RamachandranAndersonLealIsraelachvili2010_Langmuir}.  Under a strong
adhesion, however, the vesicle membranes in the contact region buckle
and form a sigmoidal shape  that has been observed in RBC doublet as
well~\cite{Ziherl2007_PRL, ZiherlSvetina2007_PNAS,
FlormannAouane2017_SciReports}.  An external electric field is also able
to buckle a vesicle membrane that is adhered to a solid
substrate~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
